### 2019-10-28 MSC-ReadingCourse.tex
initial commit

\documentclass[
	11pt,
	aspectratio=169,
]{beamer}

% Setting the colors
\hypersetup{
	colorlinks,
	citecolor=cyan,
	linkcolor=.,
	urlcolor=cyan
}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Remove these 2 lines
\usepackage[english]{babel}
\usepackage{blindtext}

% Defining a color
\usepackage{xcolor}
\definecolor{uwo-purple}{HTML}{4F2683}
\definecolor{uwo-gray}{HTML}{807F83}

% Refs
\usepackage[backend=bibtex,style=alphabetic]{biblatex}
\addbibresource{refs.bib}

% Phonetic characters
\usepackage{tipa}
\usepackage{tipx}

\usetheme{CambridgeUS}

% Customizing the template
\setbeamercolor{frametitle}{fg=uwo-purple}
\setbeamercolor{title}{fg=uwo-purple}
\setbeamercolor{palette primary}{fg=black, bg=uwo-purple!30!white}
\setbeamercolor{palette secondary}{fg=black, bg=uwo-purple!20!white}
\setbeamercolor{palette tertiary}{bg=uwo-purple}

\begin{document}
	\author{Amir HaghighatiMaleki}
	\title{Design/Cybernetics: Two Sides of One Coin}
	\subtitle{Reading Course Presentation}
	\logo{\includegraphics[width=0.7cm]{resources/uwo-purple.png}}
	\institute{Insight Lab}
	\date{\today}
	\subject{Reading Course Presentation}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
	\begin{frame}
		\maketitle
		\centering\tiny\hyperlink{http://insight.uwo.ca}{insight.uwo.ca}\\
		\centering\tiny\hyperlink{mailto:ahaghig3@uwo.ca}{ahaghig3@uwo.ca}
	\end{frame}

\begin{frame}
	\textit{\rm``The progress of knowledge is at the same time the progress of ignorance.''}\\
	--- Edgar Morin \cite{morin_1992} \\
	\vspace{0.4cm}
	\textit{\rm``The very act of focusing prevents us from seeing.''}\\
	--- ?? \\
	\vspace{0.4cm}
	\textit{\rm``We do not see what we do not see, and what we do not see does not exist.''}\\
	--- Humberto R. Maturana and Francisco J. Varela \cite{maturana_varela_1987}\\
	\vspace{0.4cm}
	\textit{\rm``The only way to overcome second-order deficiencies is with therapies of second order.''}\\
	--- Heinz von Foerster \cite{vonFoerster_2003}\\
	\vspace{0.4cm}
	\begin{figure}
		\centering
		\href{https://anewage.github.io}{
			\includegraphics[width=2cm]{resources/anewage_github_io.png}
		}
	\end{figure}
\end{frame}

\section*{Prolouge}
\begin{frame}
	\frametitle{Prologue I}
	\begin{columns}
		\column{0.3\textwidth}
			\begin{figure}
				\includegraphics[height=0.7\textheight]{resources/man.png}
			\end{figure}
		\column{0.3\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{resources/liar.jpg}
			\end{figure}
		\column{0.3\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{resources/chickenegg.jpg}
			\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
\frametitle{Prologue II}
	{\textbf{Gödel's incompleteness} theorems can be summarized as: \\
		It is impossible to construct a theoretical language that will not \textcolor{teal}{close on itself}, with the result that there are statements that are \textcolor{teal}{undecidable} in that language.} \\
	\vspace{0.5cm}
	{In other words: There are things that you \textcolor{teal}{cannot explain within a paricular language}.}

\end{frame}

\section*{Overview}
	\begin{frame}
		\frametitle{Agenda}
		\tableofcontents
	\end{frame}

\section{Introduction}
	\subsection{Definitions}
		\begin{frame}
%			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics}
			\framesubtitle{The Root of the Word}
			\textbf{Cybernetics} (\textbackslash \textipa{saI\texttt{}b@r"netIks}\textbackslash):
			\begin{itemize}
				\item<1-> From Greek `kybernetes': `\textcolor{teal}{steersman}', `kybernan': `to steer or pilot a ship, direct as a pilot'
				\item<2-> Is about having a goal and taking action to achieve that goal
				\item<3-> The art of steering \cite{pangaro_web}:
			\end{itemize}
			\centering\includegraphics<3>[width=7.2cm]{./resources/steering1.png}
			\centering\includegraphics<4>[width=7.2cm]{./resources/steering2.png}
			\centering\includegraphics<5>[width=7.2cm]{./resources/steering3.png}
			\centering\includegraphics<6>[width=7.2cm]{./resources/steering4.png}
			\centering\includegraphics<7>[width=7.2cm]{./resources/steering5.png}
			\centering\includegraphics<8>[width=7.2cm]{./resources/steering6.png}
			\centering\includegraphics<9>[width=7.2cm]{./resources/steering7.png}
			\centering\includegraphics<10>[width=7.2cm]{./resources/steering8.png}
			\centering\includegraphics<11>[width=7.2cm]{./resources/steering9.png}
			\centering\includegraphics<12>[width=7.2cm]{./resources/steering10.png}

%			\setbeamercovered{invisible}
		\end{frame}
		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Soooo... What is Cybernetics?}
			\begin{itemize}
				\item<1->Ship of the State: The Command of a naval vessel is a metaphor for the governance of a city/state.\\
				--- Plato
				\item<2->``Cybernetique is the art of governing or the science of government.''\\
				--- André-Marie Ampère
				\item<3->``Use the word ‘cybernetics’, Norbert, because nobody knows what it means. This will always put you at an advantage in arguments.''\\
				Widely quoted; attributed to Claude Shannon in a letter to Norbert Wiener in the 1940s.
				\item<4->``The Science of Effective Organization''\\
				--- Stafford Beer
				\item<5->``The art and science of uderstanding.''\\
				--- Humerto Maturana
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Soooo... What is Cybernetics?}
			\begin{itemize}
				\item<1->``The art and science of manipulating defensible metaphors''
				--- Gordon Pask
				\item<2->``A form of cross-disciplinary thought which made it possible for members of many disciplines to communicate with each other easily in a language which all could understand''
				--- Margaret Mead
				\item<3->``That is the fascinating thing about cybernetics. You ask a couple of people to give you a definition and although you don’t get to know much about cybernetics from them, you find out a lot about the person supplying the definition, including their area of expertise, their relation to the world, their desire to play with metaphors, their enthusiasm for management, and their interest in communications or message theory.''\\
				--- Heinz von Foerster
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Soooo... What is Cybernetics?}
			\begin{itemize}
				\item A clear-cut and crisp definition is very hard to find.
				\item An entire webpage is dedicated for different definitions: \url{http://asc-cybernetics.org/definitions/}\\
			\end{itemize}
		\end{frame}

		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Will History Help?}
			\begin{itemize}
				\item<1->The storylines do not split into distinct lines of descent.
				\item<2->The storylines do not subdivide into clear phases or stages.
				\item<3->\textcolor{red}{Cybernetics' history defies neat categories and compartments}...
				\item<4->An entire webpage and a lot of diagrams can be found about the history of Cybernetics: \url{http://www.asc-cybernetics.org/foundations/timeline.htm}
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{What About Ven Diagram, Set Theory, or Any Other Categoriazation Method?!}
			\begin{itemize}
				\item<1->Everybody has a different opinion as to Cybernetics' disciplinary `slot'.
				\item<2->Each person involved in Cybernetics research, draws a new line on the territory of Cybernetics. Therefore Any map of relevant people and their timeline will fail to show the exact contexts.
				\item<3->... \textcolor{red}{Cybernetics defies neat categories and compartments}
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Cybernetics defies neat categories and compartments}
			\centering\includegraphics[height=0.7\textheight]{./resources/frustrated.png}
		\end{frame}

	\subsection{Background}
		\begin{frame}
		\frametitle{Background and Theme}
		\framesubtitle{Automaticity of Behaviour in Artificial Objects}
			\begin{columns}
				\column{0.3\textwidth}
				\begin{figure}
					\includegraphics[width=3cm]{./resources/chinesecompasscart.jpg}
					\caption{Chinese Compass Cart}
				\end{figure}
				\column{0.3\textwidth}
				\begin{figure}
					\includegraphics[width=2cm]{./resources/waterclock.jpg}
					\caption{Ctesibius's Water Clock - 300s B.C.}
				\end{figure}
				\column{0.3\textwidth}
				\begin{figure}
					\includegraphics[width=3.5cm]{./resources/flyball.png}
					\caption{James Watt's Flyball Governor - 1780s}
				\end{figure}
			\end{columns}
			\begin{itemize}
				\item<1->All tools incorporated \textcolor{teal}{self-regulating} behavior without so much attention to a specific theory.
			\end{itemize}
		\end{frame}

\section{Proposal}
\subsection{Methodology}
\begin{frame}
\frametitle{Step 1}
\framesubtitle{Overall view}
	\begin{itemize}
		\item<1->The first
		\item<2->The second
		\item<3->The last
	\end{itemize}
\end{frame}
\begin{frame}
\frametitle{Step 1 (Cont'd)}
\framesubtitle{Aspects}
\begin{enumerate}
	\item<1->The first
	\item<2->The second
	\item<3->The last
\end{enumerate}
\end{frame}
\section{References}
	\begin{frame}[t,allowframebreaks]
		\frametitle{References}
		\printbibliography
	\end{frame}

\section*{Appendix}
	\begin{frame}
		\setbeamercovered{transparent}
		\frametitle{Definition(s) of Cybernetics}
		\framesubtitle{Soooo... What is Cybernetics?}
		\begin{itemize}
			\item<1->Ship of the State: The Command of a naval vessel is a metaphor for the governance of a city/state.\\
			--- Plato (420s-340s B.C.)
			\item<2->``Cybernetique is the art of governing or the science of government.''\\
			--- André-Marie Ampère (1775-1836)
			\item<3->``Use the word ‘cybernetics’, Norbert, because nobody knows what it means. This will always put you at an advantage in arguments.''\\
			Widely quoted; attributed to Claude Shannon in a letter to Norbert Wiener in the 1940s.
		\end{itemize}
		\setbeamercovered{invisible}
	\end{frame}

\end{document}

\end{document}

### 2019-10-31 MSC-ReadingCourse.tex
add intro

@@
     	\vspace{0.4cm}
-	\textit{\rm``We do not see what we do not see, and what we do not see does not exist.''}\\
+    	\textit{\rm``We do not see what we do not see, and what we do not see seems nonexistent.''}\\
     	--- Humberto R. Maturana and Francisco J. Varela \cite{maturana_varela_1987}\\
@@
         	\vspace{0.5cm}
-	{In other words: There are things that you \textcolor{teal}{cannot explain within a paricular language}.}
+        	{Simply put: There are things that you \textcolor{teal}{cannot explain within a paricular language}.}
 
@@
     \section{Introduction}
-	\subsection{Definitions}
-		\begin{frame}
-%			\setbeamercovered{transparent}
-			\frametitle{Definition(s) of Cybernetics}
-			\framesubtitle{The Root of the Word}
+        \subsection{Initial Notes}
+            \begin{frame}{Design}
+                \framesubtitle{Basics}
+                The word \textcolor{teal}{design} has its roots in drawing and designation. \\
+        	    \textbf{As a noun} $\longrightarrow$ From Italian \textit{\rm designò}: ``to draw''\\
+        	    \textbf{As a verb} $\longrightarrow$ From Latin \textit{\rm designare}: ``to designate, to outline, to appoint''\\
+        	    \centering dē- (from, out) + signō (``to mark, to sign''). 
+            \end{frame}
+            \begin{frame}{Design}
+                \framesubtitle{Wide Range of Approaches}
+        		\begin{itemize}
+        			\item<1->Design as a complex but essentially \textbf{mechanical} action (e.g., some approaches in Software Engineering, Herbert Simon):\\
+        			    Assuming a set of specified criteria: design is generating a set of  alternatives and assessing them against the criteria
+        			\item<2-> Horst Rittle (1973) $\longrightarrow$ design is essentially for \textcolor{teal}{``wicked problems''}:
+        			\textbf{no definitive formulation}, \textbf{no stopping rule}, \textbf{no assessment criteria}
+        			\item<3->Latest attempts: \textcolor{teal}{examine the heart of the design activity} instead of \textcolor{red}{prescription} and \textcolor{red}{proscription}: design and cognition (e.g., most interdisciplinary attempts)
+        		\end{itemize}
+            \end{frame}
+            \begin{frame}{Cybernetics}
+                \framesubtitle{Basics}
         			\textbf{Cybernetics} (\textbackslash \textipa{saI\texttt{}b@r"netIks}\textbackslash):
         			\begin{itemize}
-				\item<1-> From Greek `kybernetes': `\textcolor{teal}{steersman}', `kybernan': `to steer or pilot a ship, direct as a pilot'
-				\item<2-> Is about having a goal and taking action to achieve that goal
+        				\item<1-> From Greek `kybernetes': `\textcolor{teal}{steersman}'; `kybernan': `\textcolor{teal}{to steer or pilot a ship, direct as a pilot}'
+        				\item<2-> Having a goal and taking action to achieve that goal
         				\item<3-> The art of steering \cite{pangaro_web}:
@@
         			\centering\includegraphics<12>[width=7.2cm]{./resources/steering10.png}
-
-%			\setbeamercovered{invisible}
             \end{frame}
-		\begin{frame}
-			\setbeamercovered{transparent}
-			\frametitle{Definition(s) of Cybernetics (Cont'd)}
-			\framesubtitle{Soooo... What is Cybernetics?}
+            \begin{frame}{Cybernetics}
+                \framesubtitle{Approaches}
         		\begin{itemize}
-				\item<1->Ship of the State: The Command of a naval vessel is a metaphor for the governance of a city/state.\\
-				--- Plato
-				\item<2->``Cybernetique is the art of governing or the science of government.''\\
-				--- André-Marie Ampère
-				\item<3->``Use the word ‘cybernetics’, Norbert, because nobody knows what it means. This will always put you at an advantage in arguments.''\\
-				Widely quoted; attributed to Claude Shannon in a letter to Norbert Wiener in the 1940s.
-				\item<4->``The Science of Effective Organization''\\
-				--- Stafford Beer
-				\item<5->``The art and science of uderstanding.''\\
-				--- Humerto Maturana
-			\end{itemize}
-			\setbeamercovered{invisible}
-		\end{frame}
-
-		\begin{frame}
-			\setbeamercovered{transparent}
-			\frametitle{Definition(s) of Cybernetics (Cont'd)}
-			\framesubtitle{Soooo... What is Cybernetics?}
-			\begin{itemize}
-				\item<1->``The art and science of manipulating defensible metaphors''
-				--- Gordon Pask
-				\item<2->``A form of cross-disciplinary thought which made it possible for members of many disciplines to communicate with each other easily in a language which all could understand''
-				--- Margaret Mead
-				\item<3->``That is the fascinating thing about cybernetics.
-You ask a couple of people to give you a definition and although you don’t get to know much about cybernetics from them, you find out a lot about the person supplying the definition, including their area of expertise, their relation to the world, their desire to play with metaphors, their enthusiasm for management, and their interest in communications or message theory.''\\
-				--- Heinz von Foerster
-			\end{itemize}
-			\setbeamercovered{invisible}
-		\end{frame}
-
-		\begin{frame}
-			\frametitle{Definition(s) of Cybernetics (Cont'd)}
-			\framesubtitle{Soooo... What is Cybernetics?}
-			\begin{itemize}
-				\item A clear-cut and crisp definition is very hard to find.
-				\item An entire webpage is dedicated for different definitions: \url{http://asc-cybernetics.org/definitions/}\\
+        			\item<1-> \textcolor{teal}{Control}, \textcolor{teal}{feedback}, \textcolor{teal}{communication}, \textcolor{teal}{circular causality} $\longrightarrow$ from N.
+Wiener and the transdisciplinary endeavours at Macy Conferences (1946-1953):\\
+        		    Many many forms -- applications in engineering, management, law, business, ...
+        			\item<2-> When applied recursively to examine cybernetic ideas and institutions $\longrightarrow$ \textcolor{teal}{The cybernetics of} \textbf{\textcolor{teal}{observing}} (rather than \textcolor{orange}{observed}) systems: Second-Order Cybernetics\\
+        			\textcolor{teal}{Constructive}, \textcolor{teal}{recursive}, and \textcolor{teal}{consistent} approach to cybernetics
+        			\item<3-> Important figures and institutions: Kenneth Boulding, Margaret Mead, Heinz von Foerster, Gordon Pask, Humberto Maturana, Paul Pangaro, American Society for Cybernetics, International Society for the Systems Sciences
         		\end{itemize}
             \end{frame}
-
-		\begin{frame}
-			\setbeamercovered{transparent}
-			\frametitle{Definition(s) of Cybernetics (Cont'd)}
-			\framesubtitle{Will History Help?}
+            \begin{frame}{Cybernetics}
+                \framesubtitle{Types of Systems}
+        		\begin{figure}
+        		    \centering
+        		    \includegraphics[height=0.8\textheight]{resources/systems.PNG}
+        		\end{figure}
+            \end{frame}
+            \begin{frame}{Cybernetics}
+                \framesubtitle{Systems and Interactions}
+        		\begin{figure}
+        		    \centering
+        		    \includegraphics[height=0.8\textheight]{resources/interaction.PNG}
+        		\end{figure}
+            \end{frame}
+    \section{Considerations}
+        \subsection{Design}
+            \begin{frame}{Design}
+                From this perspective, design is:
                 \begin{itemize}
-				\item<1->The storylines do not split into distinct lines of descent.
-				\item<2->The storylines do not subdivide into clear phases or stages.
-				\item<3->\textcolor{red}{Cybernetics' history defies neat categories and compartments}...
-				\item<4->An entire webpage and a lot of diagrams can be found about the history of Cybernetics: \url{http://www.asc-cybernetics.org/foundations/timeline.htm}
+                    \item<1-> Not the outcome of a process.
+                    \item<2-> Not a problem solving process.
+                    \item<3-> Not a way of facing complexity.
+                    \item<4-> An \textcolor{teal}{activity} that is carried out in the face of very complex and conflicting requirements.
                 \end{itemize}
-			\setbeamercovered{invisible}
             \end{frame}
-
-		\begin{frame}
-			\setbeamercovered{transparent}
-			\frametitle{Definition(s) of Cybernetics (Cont'd)}
-			\framesubtitle{What About Ven Diagram, Set Theory, or Any Other Categoriazation Method?!}
+        \subsection{First-Order Cybernetics}
+            \begin{frame}{Control}
                 \begin{itemize}
-				\item<1->Everybody has a different opinion as to Cybernetics' disciplinary `slot'.
-				\item<2->Each person involved in Cybernetics research, draws a new line on the territory of Cybernetics.
-Therefore Any map of relevant people and their timeline will fail to show the exact contexts.
-				\item<3->... \textcolor{red}{Cybernetics defies neat categories and compartments}
+                    \item<1-> Control \neq Restriction
+                    \item<2-> Control = Guide towards better performance
+                    \begin{itemize}
+                        \item Goal or Intention
+                        \item Means of communication of \textcolor{teal}{the intention} and \textcolor{teal}{the action of control} to an actor
                     \end{itemize}
-			\setbeamercovered{invisible}
+                    \item<3-> What constitutes control in a system that \textcolor{teal}{enables} rather than \textcolor{red}{restricts}?
+                \end{itemize}
             \end{frame}
-
-		\begin{frame}
-			\frametitle{Definition(s) of Cybernetics (Cont'd)}
-			\framesubtitle{Cybernetics defies neat categories and compartments}
-			\centering\includegraphics[height=0.7\textheight]{./resources/frustrated.png}
+            \begin{frame}{Law of Requisite Variety (First Law of Cybernetics)}
+                \begin{itemize}
+                    \item<1-> Variety = the number of all possible states for a system
+                    \item<2-> Ross Ashby's law of \textcolor{teal}{Requisite Variety}: \\
+                        The system that is in control must have at least as many states as the system to be controlled.
+                    \item<3-> Not being restrictive $\longrightarrow$ The controller must have requisite variety.
+                \end{itemize}
             \end{frame}
-
-	\subsection{Background}
-		\begin{frame}
-		\frametitle{Background and Theme}
-		\framesubtitle{Automaticity of Behaviour in Artificial Objects}
+            \begin{frame}{Back to Control}
                 \begin{columns}
-				\column{0.3\textwidth}
+                    \column{0.6\textwidth}
+                        \begin{itemize}
+                            \item<1-> In circular systems, which element controls and which is being controlled?
+                            \item<2-> Control is \textcolor{red}{neither} in one element \textcolor{red}{nor} the other; it \textcolor{teal}{emerges} as a result of their \textcolor{teal}{interaction}.
+                            \item<3-> Circularity is embodied in the role of the observer in cybernetic systems:\\
+                            $\longrightarrow$ The observer cannot be inactive, or there would be no system.
+                        \end{itemize}
+                    \column{0.4\textwidth}
                     \begin{figure}
-					\includegraphics[width=3cm]{./resources/chinesecompasscart.jpg}
-					\caption{Chinese Compass Cart}
-				\end{figure}
-				\column{0.3\textwidth}
-				\begin{figure}
-					\includegraphics[width=2cm]{./resources/waterclock.jpg}
-					\caption{Ctesibius's Water Clock - 300s B.C.}
-				\end{figure}
-				\column{0.3\textwidth}
-				\begin{figure}
-					\includegraphics[width=3.5cm]{./resources/flyball.png}
-					\caption{James Watt's Flyball Governor - 1780s}
+        		        \centering\includegraphics[height=0.6\textheight]{resources/thermostate.PNG}
         		    \end{figure}
                 \end{columns}
+            \end{frame}
+        \subsection{Circularity and Second-Order Cybernetics}
+            \begin{frame}{Subject/Metasubject}
+                \begin{columns}
+                    \column{0.5\textwidth}
                         \begin{itemize}
-				\item<1->All tools incorporated \textcolor{teal}{self-regulating} behavior without so much attention to a specific theory.
+                            \item<1-> Mathematics:\\
+                                A Distinct field worthy of consideration in its own right and by its own criteria.\\
+                                Its \textcolor{teal}{abstraction} $\longrightarrow$ when applied to other subjects, \textcolor{teal}{casts light} upon them and \textcolor{teal}{enhances} our understanding.
+                            \item<2-> Cybernetics $\sim$ Mathematics\\
+                                Second-Order Cybernetics $\longrightarrow$ It is both its own subject and its own metasubject.
+                            \item<3-> Design $\sim$ Cybernetics\\
+                                Studied in the light of its own criteria:\\
+                                (recursive) design of design
                         \end{itemize}
+                    \column{0.5\textwidth}
+                        \begin{itemize}
+                            \item<4-> Cybernetics: \textcolor{teal}{structure} and \textcolor{teal}{form} to construct \textcolor{orange}{individual} meaning and understanding\\
+                                Leaves \textcolor{teal}{meaning} and \textcolor{teal}{emotion} to the observer (\textcolor{red}{private})\\
+                                $\longrightarrow$ Supports structures that support our \textcolor{teal}{autonomy} and \textcolor{teal}{freedom}\\
+                                $\longrightarrow$ (recursive) \textcolor{teal}{Support of support}
+                        \end{itemize}
+                \end{columns}
             \end{frame}
-
-\section{Proposal}
-\subsection{Methodology}
+            \subsubsection{Subjective/Objective}
+                \begin{frame}{Subjective/Objective}
+                    \framesubtitle{Observer Incorporated? \cite{vonFoerster_2003}}
+                    \begin{columns}
+                        \column{0.7\textwidth}
+                            \begin{itemize}
+                                \item<1-> Feedback $\longrightarrow$ an active actor (observer)
+                                \item<2-> A description (observation) $\implies$ a describer (observer)
+                                    \begin{enumerate}
+                                        \item Observations are \textcolor{red}{not absolute} but \textcolor{teal}{relative} to the observer's point of view (Einstein)
+                                        \item Observations \textcolor{teal}{affect} the observer to obliterate her hope of prediction (Heisenberg)
+                                    \end{enumerate}
+                                \item<3-> A description (of the world) $\implies$ a universal reality
+                                \item<4-> A description (theory) of a describer has to account the \textcolor{teal}{describer} herself and her \textcolor{teal}{expression of the description}.
+                            \end{itemize}
+                        \column{0.3\textwidth}
+                            ``I am a liar'' -- true or false? \\
+                            \begin{figure}
+                				\includegraphics[height=0.5\textheight]{resources/man.png}
+                			\end{figure}
+                			``The reality is only my imagination'' (?)
+                    \end{columns}
+                \end{frame}
+            \subsubsection{Recursion/Repetition}
                 \begin{frame}
-\frametitle{Step 1}
-\framesubtitle{Overall view}
+                    \frametitle{Recursion/Repetition}
+                    \framesubtitle{Heinz von Foerster's Eigen Forms (structures, functions, objects, behaviours, and values)}
+                    Tokens for stable behaviour: tokens for Eigen functions (Recursive Function Theory)\\
+                    Examples:
                     \begin{itemize}
-		\item<1->The first
-		\item<2->The second
-		\item<3->The last
+                        \item<1-> $f(x)= {{x}\over{2}} +1$\\
+                            \fontsize{8}{9.2}\selectfont
+                            \begin{columns}
+                                \column{0.1\textwidth}
+                                \column{0.4\textwidth}
+                                    $\longrightarrow x_0=4$\\
+                                    $\longrightarrow x_1=f(x_0) = {{4}\over{2}} + 1 = 3$ \\
+                                    $\longrightarrow x_2=f(x_1) = {{3}\over{2}} + 1 = 2.5$ \\
+                                    $\longrightarrow x_3=f(x_2) = {{2.5}\over{2}} + 1 = 2.25$\\
+                                    $\longrightarrow x_4=f(x_3) = {{2.25}\over{2}} + 1 = 2.125$\\
+                                    $\longrightarrow x_5=f(x_4) = {{2.125}\over{2}} + 1 = 2.063$\\
+                                    $\longrightarrow x_{11}=f(x_{10}) = {{x_{10}}\over{2}} + 1 = 2.001$\\
+                                    $\longrightarrow x_\infty=f(x_\infty) = {{x_\infty}\over{2}} + 1 = \textcolor{red}{2.000}$\\
+                                \column{0.5\textwidth}
+                                    $\longrightarrow x_0=1$\\
+                                    $\longrightarrow x_1=f(x_0) = {{1}\over{2}} + 1 = 1.5$ \\
+                                    $\longrightarrow x_2=f(x_1) = {{1.5}\over{2}} + 1 = 1.75$ \\
+                                    $\longrightarrow x_3=f(x_2) = {{1.75}\over{2}} + 1 = 1.875$\\
+                                    $\longrightarrow x_8=f(x_7) = {{x_7}\over{2}} + 1 = 1.996$\\
+                                    $\longrightarrow x_{10}=f(x_9) = {{x_9}\over{2}} + 1 = 1.999$\\
+                                    $\longrightarrow x_\infty=f(x_\infty) = {{x_\infty}\over{2}} + 1 = \textcolor{red}{2.000}$\\ 
+                            \end{columns}
+                        \item<2-> $2$ is the \textcolor{teal}{Eigen value} of $f$
                     \end{itemize}
@@
                 \begin{frame}
-\frametitle{Step 1 (Cont'd)}
-\framesubtitle{Aspects}
-\begin{enumerate}
-	\item<1->The first
-	\item<2->The second
-	\item<3->The last
-\end{enumerate}
+                    \frametitle{Recursion/Repetition}
+                    \framesubtitle{Heinz von Foerster's Eigen Forms (structures, functions, objects, behaviours, and values)}
+                    Tokens for stable behaviour: tokens for Eigen functions (Recursive Function Theory)\\
+                    Examples:
+                    \begin{itemize}
+                        \item<1-> $f(g)= {{d}\over{dx}}g$\\
+                            $exp=e^x \implies f(exp) = {{d}\over{dx}}exp = exp$\\
+                            $\longrightarrow f(f(f(...f(f(exp))...))) = exp$\\
+                        \item<2-> $exp = e^x$ is the \textcolor{teal}{Eigen function} for operator $f$
+                    \end{itemize}
                 \end{frame}
+                \begin{frame}
+                    \frametitle{Recursion/Repetition}
+                    \framesubtitle{Heinz von Foerster's Eigen Forms (structures, functions, objects, behaviours, and values)}
+                    Tokens for stable behaviour: tokens for Eigen functions (Recursive Function Theory)\\
+                    Examples:
+                    \begin{itemize}
+                        \item<1-> ``This sentence has ... letters'' $\implies$ \textcolor{red}{THIRTY-ONE} or \textcolor{red}{THIRTY-THREE}\\
+                        ``This sentence \textcolor{blue}{`This sentence has THIRTY-ONE letters'} has ... letters'' $\implies$ \textcolor{red}{THIRTY-ONE}\\
+                        ``This sentence \textcolor{purple}{`This sentence \textcolor{blue}{<This sentence has THIRTY-ONE letters>} has THIRTY-ONE letters'} has ...
+letters'' $\implies$ \textcolor{red}{THIRTY-ONE} \\
+                        \vspace{0.7cm}
+                        \item<2-> ``This sentence consists of ... letters'' $\implies$ THIRTY-NINE \\
+                        ``This sentence is composed of ... letters'' $\implies$ $\nexists$
+                    \end{itemize}
+                \end{frame}
+                \begin{frame}{Recursion/Repetition}
+                    \framesubtitle{Learning, Autopoiesis, Eigen Forms, and Ranulph Glanville's Object Theory}
+                    \begin{figure}
+                        \centering\includegraphics[width=0.7\textwidth]{resources/recursion.png}
+                    \end{figure}
+                \end{frame}
+            \subsubsection{Conversation}
+                \begin{frame}{Conversation Model \cite{pangaro_web}}
+                    \framesubtitle{Based on Gordon Pask's Conversation Theory (1976)}
+                    \centering\includegraphics<1>[page=23, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<2>[page=24, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<3>[page=25, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<4>[page=26, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<5>[page=27, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<6>[page=28, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<7>[page=29, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<8>[page=30, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<9>[page=31, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<10>[page=32, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<11>[page=33, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<12>[page=34, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                \end{frame}
+                \begin{frame}{The Theory}
+                    \framesubtitle{Gordon Pask's Conversation Theory (1976)}
+                    \centering\includegraphics<1>[page=99, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                \end{frame}
+                \begin{frame}{Mental Models \cite{dubberly2009}}
+                    \centering \includegraphics[width=\textwidth]{resources/models1.PNG}
+                \end{frame}
+                \begin{frame}{Mental Models \cite{dubberly2009}}
+                    \framesubtitle{Learning as Forming and Reforming Models}
+                    \centering\includegraphics[width=0.75\textwidth]{resources/learning.PNG}
+                \end{frame}
+                \begin{frame}{Mental Models \cite{dubberly2009}}
+                    \framesubtitle{TV dramas shape culture or culture inspire TV dramas?}
+                    \centering\includegraphics<1->[width=0.75\textwidth]{resources/models4.PNG} \\
+                    \centering\includegraphics<2->[width=0.25\textwidth]{resources/chickenegg.jpg}
+                \end{frame}
+                \begin{frame}{Mental Models \cite{dubberly2009}}
+                    \framesubtitle{Agreement}
+                    \centering\includegraphics[width=0.5\textwidth]{resources/models5.PNG}
+                \end{frame}
+                \begin{frame}{Why Conversation? \cite{pangaro_web}}
+                    \centering\includegraphics<1>[page=35, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<2>[page=36, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                    \centering\includegraphics<3>[page=37, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+                \end{frame}
+    \section{The Harmony}
+        \
+
 \section{References}
-	\begin{frame}[t,allowframebreaks]
+	\begin{frame}[allowframebreaks]
 		\frametitle{References}
@@
 	\end{frame}
+	\begin{frame}{NOT a Conversation}
+        \framesubtitle{Shannon's Model of Transmission}
+        \begin{figure}
+            \centering\includegraphics[width=0.8\textwidth]{resources/transmission.PNG}
+        \end{figure}
+        This model does not scaffold novelty, is pure mechanical, and does not support learning.
+    \end{frame}
+    \begin{frame}{Mental Models}
+        \framesubtitle{Shaping and re-Shaping}
+            \centering\includegraphics<1>[width=0.75\textwidth]{resources/models6.PNG}
+            \centering\includegraphics<2>[height=0.77\textheight]{resources/models7.PNG}
+    \end{frame}
 
 \end{document}
-
-\end{document}

### 2019-10-31 junk.tex
add intro

    \subsection{Cybernetics}
        \subsubsection{Definitions}
        \subsubsection{Background}
        \subsubsection{Second-Order Cybernetics}
    \subsection{The Connection}
        \subsubsection{Design for Cybernetics}
        \subsubsection{Cybernetics for Design}

\section{Introduction}
	\subsection{Cybernetics: Definitions}
		\begin{frame}
%			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics}
			\framesubtitle{The Root of the Word}
			\textbf{Cybernetics} (\textbackslash \textipa{saI\texttt{}b@r"netIks}\textbackslash):
			\begin{itemize}
				\item<1-> From Greek `kybernetes': `\textcolor{teal}{steersman}'; `kybernan': `\textcolor{teal}{to steer or pilot a ship, direct as a pilot}'
				\item<2-> Having a goal and taking action to achieve that goal
				\item<3-> The art of steering \cite{pangaro_web}:
			\end{itemize}
			\centering\includegraphics<3>[width=7.2cm]{./resources/steering1.png}
			\centering\includegraphics<4>[width=7.2cm]{./resources/steering2.png}
			\centering\includegraphics<5>[width=7.2cm]{./resources/steering3.png}
			\centering\includegraphics<6>[width=7.2cm]{./resources/steering4.png}
			\centering\includegraphics<7>[width=7.2cm]{./resources/steering5.png}
			\centering\includegraphics<8>[width=7.2cm]{./resources/steering6.png}
			\centering\includegraphics<9>[width=7.2cm]{./resources/steering7.png}
			\centering\includegraphics<10>[width=7.2cm]{./resources/steering8.png}
			\centering\includegraphics<11>[width=7.2cm]{./resources/steering9.png}
			\centering\includegraphics<12>[width=7.2cm]{./resources/steering10.png}

%			\setbeamercovered{invisible}
		\end{frame}
		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{What is?}
			\begin{itemize}
				\item<1->Ship of the State: The Command of a naval vessel is a metaphor for the governance of a city/state.\\
				--- Plato
				\item<2->``Cybernetique is the art of governing or the science of government.''\\
				--- André-Marie Ampère
				\item<3->``Use the word ‘cybernetics’, Norbert, because nobody knows what it means. This will always put you at an advantage in arguments.''\\
				Widely quoted; attributed to Claude Shannon in a letter to Norbert Wiener in the 1940s.
				\item<4->``The Science of Effective Organization''\\
				--- Stafford Beer
				\item<5->``The art and science of uderstanding.''\\
				--- Humerto Maturana
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{What is?}
			\begin{itemize}
				\item<1->``The art and science of manipulating defensible metaphors''
				--- Gordon Pask
				\item<2->``A form of cross-disciplinary thought which made it possible for members of many disciplines to communicate with each other easily in a language which all could understand''
				--- Margaret Mead
				\item<3->``That is the fascinating thing about cybernetics. You ask a couple of people to give you a definition and although you don’t get to know much about cybernetics from them, you find out a lot about the person supplying the definition, including their area of expertise, their relation to the world, their desire to play with metaphors, their enthusiasm for management, and their interest in communications or message theory.''\\
				--- Heinz von Foerster
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{What is?}
			\begin{itemize}
				\item A clear-cut and crisp definition is very hard to find.
				\item An entire webpage is dedicated for different definitions: \url{http://asc-cybernetics.org/definitions/}\\
			\end{itemize}
		\end{frame}

		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Will History Help?}
			\begin{itemize}
				\item<1->The storylines do not split into distinct lines of descent.
				\item<2->The storylines do not subdivide into clear phases or stages.
				\item<3->\textcolor{red}{Cybernetics' history defies neat categories and compartments}...
				\item<4->An entire webpage and a lot of diagrams can be found about the history of Cybernetics: \url{http://www.asc-cybernetics.org/foundations/timeline.htm}
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\setbeamercovered{transparent}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{What About Ven Diagram, Set Theory, or Any Other Categoriazation Method?!}
			\begin{itemize}
				\item<1->Everybody has a different opinion as to Cybernetics' disciplinary `slot'.
				\item<2->Each person involved in Cybernetics research, draws a new line on the territory of Cybernetics. Therefore Any map of relevant people and their timeline will fail to show the exact contexts.
				\item<3->... \textcolor{red}{Cybernetics defies neat categories and compartments}
			\end{itemize}
			\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
			\frametitle{Definition(s) of Cybernetics (Cont'd)}
			\framesubtitle{Cybernetics defies neat categories and compartments}
			\centering\includegraphics[height=0.7\textheight]{./resources/frustrated.png}
		\end{frame}

	\subsection{Cybernetics: Background}
		\begin{frame}
		\frametitle{Classic Examples}
		\framesubtitle{Automaticity of Behaviour in Artificial Objects}
			\begin{columns}
				\column{0.3\textwidth}
				\begin{figure}
					\includegraphics[width=3cm]{./resources/chinesecompasscart.jpg}
					\caption{Chinese Compass Cart}
				\end{figure}
				\column{0.3\textwidth}
				\begin{figure}
					\includegraphics[width=2cm]{./resources/waterclock.jpg}
					\caption{Ctesibius's Water Clock - 300s B.C.}
				\end{figure}
				\column{0.3\textwidth}
				\begin{figure}
					\includegraphics[width=3.5cm]{./resources/flyball.png}
					\caption{James Watt's Flyball Governor - 1780s}
				\end{figure}
			\end{columns}
			\begin{itemize}
				\item<1->All tools incorporated \textcolor{teal}{self-regulating} behavior without so much attention to a specific theory.
			\end{itemize}
		\end{frame}

		\begin{frame}
		\setbeamercovered{transparent}
		\frametitle{Through Systems Perspective}
		\framesubtitle{Self-Regulation Mechanisms; Machine/Organism Similarity}
			\begin{columns}
				\column{0.7\textwidth}
			        \begin{itemize}
				        \item<1->This model would remain evident in later models of \textcolor{teal}{feedback}.
				        \item<2->This model would remain evident in later models of \textcolor{teal}{feedback}.
			        \end{itemize}
				\column{0.2\textwidth}
				\begin{figure}
					\includegraphics[width=3cm]{./resources/lincke_mechanical_relay.PNG}
				\end{figure}
			\end{columns}
		\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
    		\setbeamercovered{transparent}
    		\frametitle{Homeostasis}
    		\framesubtitle{Dynamic Systems' Self-Maintained Stability}
    		Introduction to Homeostasis...
    		\setbeamercovered{invisible}
		\end{frame}

		\begin{frame}
    		\setbeamercovered{transparent}
    		\frametitle{Teleological Implications of `Regulation'}
    		\framesubtitle{Aristotelian Dictatorship is Being Attacked!}
    		Arturo Rosenblueth (1937):\\
    		\begin{columns}
    		    \column{0.7\textwidth}
    		        \begin{itemize}
    		            \item<1->Regulation $\longrightarrow$ Prospective \textcolor{teal}{goal} or \textcolor{teal}{purpose}
    		            \item<2->Purposeful behaviour:
    		                \begin{itemize}
    		                    \item Feed-back (teleological): positive or negative
    		                    \item Non-feed-back (non-teleological)
    		                \end{itemize}
		                \item<3->All purposeful behaviour must require negative feed-back
		                \item<4->Purposefulness is independent of causality, effective or final
    		        \end{itemize}
    		    \column{0.3\textwidth}
    		        \begin{figure}
					    \includegraphics[width=3cm]{./resources/4cause.png}
				    \end{figure}
    		\end{columns}
    		\setbeamercovered{invisible}
		\end{frame}
	\subsection{Cybernetics of Cybernetics: Second Order}
		\begin{frame}
		\end{frame}
	\subsection{Design}

### 2019-10-31 MSC-ReadingCourse.tex
minor updates
update intro

@@
         			\textcolor{teal}{Constructive}, \textcolor{teal}{recursive}, and \textcolor{teal}{consistent} approach to cybernetics
-        			\item<3-> Important figures and institutions: Kenneth Boulding, Margaret Mead, Heinz von Foerster, Gordon Pask, Humberto Maturana, Paul Pangaro, American Society for Cybernetics, International Society for the Systems Sciences
+        			\item<3-> Important figures and institutions: Kenneth Boulding, Margaret Mead, Heinz von Foerster, Gordon Pask, Humberto Maturana, Paul Pangaro, American Society for Cybernetics, International Society for the Systems Sciences, ...
         		\end{itemize}
@@
             \begin{frame}{Cybernetics}
-                \framesubtitle{Types of Systems}
+                \framesubtitle{Types of Systems \cite{pangaro_web}}
         		\begin{figure}
         		    \centering
-        		    \includegraphics[height=0.8\textheight]{resources/systems.PNG}
-        		\end{figure}
-            \end{frame}
-            \begin{frame}{Cybernetics}
-                \framesubtitle{Systems and Interactions}
-        		\begin{figure}
-        		    \centering
-        		    \includegraphics[height=0.8\textheight]{resources/interaction.PNG}
+        		    \includegraphics[height=0.75\textheight]{resources/systems.PNG}
         		\end{figure}
@@
                     \item<2-> Ross Ashby's law of \textcolor{teal}{Requisite Variety}: \\
-                        The system that is in control must have at least as many states as the system to be controlled.
+                        In order to maintain its viability, the system that is in control must have at least as many states as the system to be controlled.
                     \item<3-> Not being restrictive $\longrightarrow$ The controller must have requisite variety.
@@
 	\end{frame}
-	\begin{frame}{NOT a Conversation}
+	\begin{frame}{What is NOT a Conversation?}
         \framesubtitle{Shannon's Model of Transmission}
@@
     \end{frame}
-
+    \begin{frame}{Interaction}
+        \framesubtitle{Configurations \cite{pangaro_web}}
+		\begin{figure}
+		    \centering
+		    \includegraphics[height=0.75\textheight]{resources/interaction.PNG}
+		\end{figure}
+    \end{frame}
 \end{document}

### 2019-11-01 MSC-ReadingCourse.tex
final changes

@@
 % Refs
+\usepackage{csquotes}
 \usepackage[backend=bibtex,style=alphabetic]{biblatex}
@@
         	{Simply put: There are things that you \textcolor{teal}{cannot explain within a paricular language}.}
-
         \end{frame}
 
-    \section*{Overview}
-    	\begin{frame}
-		\frametitle{Agenda}
-    		\tableofcontents
-    	\end{frame}
-
-    \section{Introduction}
+    \section{What?}
         \subsection{Initial Notes}
@@
                 \begin{itemize}
-                    \item<1-> Control \neq Restriction
-                    \item<2-> Control = Guide towards better performance
+                    \item<1-> Control $\neq$ Restriction
+                    \item<2-> Control $=$ Guide towards better performance\\
+                    $\equiv$ Enabling for effectiveness\\
+                    $\equiv$ Effective management (Stafford Beer)
                     \begin{itemize}
-                        \item Goal or Intention
+                        \item Goal or intention
                         \item Means of communication of \textcolor{teal}{the intention} and \textcolor{teal}{the action of control} to an actor
@@
             \subsubsection{Subjective/Objective}
-                \begin{frame}{Subjective/Objective}
-                    \framesubtitle{Observer Incorporated? \cite{vonFoerster_2003}}
+                \begin{frame}
+                    \frametitle{Subjective/Objective}
+                    \framesubtitle{Observer Incorporated?}
                     \begin{columns}
@@
                             ``I am a liar'' -- true or false? \\
-                            \begin{figure}
-                				\includegraphics[height=0.5\textheight]{resources/man.png}
-                			\end{figure}
+            				\centering\includegraphics[height=0.5\textheight]{./resources/man.png}\\
                 			``The reality is only my imagination'' (?)
@@
                                     $\longrightarrow x_{11}=f(x_{10}) = {{x_{10}}\over{2}} + 1 = 2.001$\\
-                                    $\longrightarrow x_\infty=f(x_\infty) = {{x_\infty}\over{2}} + 1 = \textcolor{red}{2.000}$\\
+                                    $\longrightarrow x_\infty=f(x_\infty) = {{x_\infty}\over{2}} + 1 =$ \textcolor{red}{$2.000$}\\
                                 \column{0.5\textwidth}
@@
                                     $\longrightarrow x_{10}=f(x_9) = {{x_9}\over{2}} + 1 = 1.999$\\
-                                    $\longrightarrow x_\infty=f(x_\infty) = {{x_\infty}\over{2}} + 1 = \textcolor{red}{2.000}$\\ 
+                                    $\longrightarrow x_\infty=f(x_\infty) = {{x_\infty}\over{2}} + 1 =$ \textcolor{red}{$2.000$}\\ 
                             \end{columns}
-                        \item<2-> $2$ is the \textcolor{teal}{Eigen value} of $f$
+                        \item<2-> 2 is the \textcolor{teal}{Eigen value} of $f$
                     \end{itemize}
@@
                         \item<2-> ``This sentence consists of ... letters'' $\implies$ THIRTY-NINE \\
-                        ``This sentence is composed of ... letters'' $\implies$ $\nexists$
+                        ``This sentence is composed of ... letters'' $\implies \nexists$
                     \end{itemize}
@@
                     \end{figure}
+                \end{frame}
+                \begin{frame}{Recursion/Repetition}
+                    \framesubtitle{Viable Systems Model (Stafford Beer)}
+                    \begin{columns}
+                        \column{0.5\textwidth} \centering\includegraphics[height=0.8\textheight]{resources/brain_spinalCord.jpg}
+                        \column{0.5\textwidth} \centering\includegraphics[height=0.75\textheight]{resources/VSM.png}
+                    \end{columns}
                 \end{frame}
@@
                 \begin{frame}{Mental Models \cite{dubberly2009}}
+                    \framesubtitle{Abductive Reasoning}
                     \centering \includegraphics[width=\textwidth]{resources/models1.PNG}
@@
                 \end{frame}
-                \begin{frame}{Why Conversation? \cite{pangaro_web}}
+    \section{The Harmony}
+        \subsection{Determinism}
+            \begin{frame}{Cybernetics, Design, and Determinism}
+            \framesubtitle{Variety and Design: The Undefinable}
+    		    \begin{itemize}
+                    \item<1-> The vast universe is nevertheless \textcolor{red}{finite}\\
+    		        $\implies$ computing capacity \textcolor{red}{always} has a limit (even the most powerful conceivable systems)
+    		        \item<2-> Even simple problems can very rapidly become \textcolor{red}{transcomputable}.\\
+    		            Ex: configurations of lightbulbs on a 20$\times$20 matrix
+    		            Design almost always faces transcomputable problems.
+		            \item<3-> The new: something that is not inherent in the existing \\
+		            $\implies$ not predictable $\equiv$ not dependent on any variable $\equiv$ not emergent \\
+    		        The Undefinable: Impossible to expect to \textcolor{red}{accurately} define a design problem.
+    		    \end{itemize}
+            \end{frame}
+            \begin{frame}{Cybernetics, Design, and Determinism}
+            \framesubtitle{Variety and Design: Definability and Variety}
+    		    \begin{itemize}
+    		        \item<1-> Viable Control = Effective Management = Regulation = Stability = Sustainability = ... \\
+    		        $\implies$ \textcolor{teal}{Requisite Variety} (controll\textcolor{red}{er} $\leqslant$ controll\textcolor{red}{ed})
+    		        \item<2-> Second-Order Cybernetics: Control is emergent (distinctiveness of controlled and controller is arbitrary).\\
+        		        $\longrightarrow$ For second-order systems: stability $\equiv$ the variety can only be \textcolor{teal}{the same}.
+                    \item<3-> Defining a problem = modeling = controlling (without restricting) the performance of a system\\
+                    \item<4-> What if the system (the problem under study) is transcomputable?
+                        \begin{enumerate}
+                            \item<5-> Changing the definitions of the context under which we chose the states (simplifying)
+                            \item<6-> Transforming the notion of control: control-as-restricting
+                        \end{enumerate}
+    		    \end{itemize}
+            \end{frame}
+            \begin{frame}{Cybernetics, Design, and Determinism}
+            \framesubtitle{Variety and Design: Unmanageability and Creativity}
+    		    \begin{itemize}
+    		        \item<1-> Being in control = Defining the range of possible (what will be considered)
+    		        \item<2-> When I am in control $\implies$ I restrict the world to what I can imagine or permit\\
+    		            $\implies$ I support a predetermination of what-is and what-might-be and aim towards predetermined goals.
+		            \item<3-> Ex: Deciding to go to a restaurant:\\
+		                    If I choose (restrict) $\longrightarrow$ reflections of my taste, knowledge and ignorance.\\
+		                    If I let others choose $\longrightarrow$ I can find new experiences.
+                    \item<4-> Benefit of not having enough variety to control the system\\
+                    $\longrightarrow$ Discover \textcolor{teal}{the unexpected} and \textcolor{teal}{the novel}
+                    \item<5-> Not restricting the future considerations to current knowledge: Experiencing the vast unknown
+    		    \end{itemize}
+            \end{frame}
+        \subsection{Design As Done}
+            \begin{frame}{Design As Done}
+            \framesubtitle{Design as a Conversation with self (and others)}
+    		    \begin{itemize}
+    		        \item<1-> We look and then we draw
+    		        \item<1-> We see something new, not previously intended
+    		        \item<2-> Conversation requires switching roles: \textcolor{teal}{pendulum}
+    		        \item<3-> Meanings are private $\implies$ understandings are different: \textcolor{teal}{novelty}
+    		        \item<4-> Agree to agree; or agree to disagree
+    		        \item<4-> Test for understanding: Consistency of what I hear and what I say
+    		        \item<5-> $\longrightarrow$ Increasing the \textcolor{teal}{variety} of the ``repertoire'' of the designer
+    		        \item<6-> Recursion, role switching $\longrightarrow$ understand \textcolor{red}{well enough} to face \textcolor{red}{complexity}
+		            \item<7-> We \textcolor{teal}{construct} our understanding
+    		    \end{itemize}
+            \end{frame}
+            \begin{frame}{Design As Done}
+            \framesubtitle{Conversation, Objects, Eigen forms, and Autonomy}
+    		    \begin{itemize}
+    		        \item<1-> Conversation with self
+    		        \item<2-> Autopoietic systems: Create conditions to create themselves; continue to \textcolor{teal}{reproduce} themselves in the environment
+    		        \item<3-> Eigen forms: a system can operate on its own output, \textcolor{teal}{treating} it as an input.
+    		        \item<4-> Designers: create the conditions in which the design outcome can come into being; continue the design act to reach a constant outcome (details  may be enriched).
+    		        \item<5-> Children: grow to become their own persons
+    		        \item<6-> $\longrightarrow$ \textcolor{red}{Autonomy = Organizational Closure}
+    		    \end{itemize}
+            \end{frame}
+            \begin{frame}{Design As Done}
+            \framesubtitle{Conversation as Design}
+    		    \begin{itemize}
+    		        \item<1-> Design translated once more: \textcolor{red}{Wandering}
+                    \item<2-> Once arrived, we can make sense of the progress. (the ``solution'' defines the ``problem'')
+                    \item<3-> Arriving and stopping? Eigen forms? \textcolor{teal}{Well enough: stable form}.
+                    \item<4-> Stopping and re-starting? 
+                    \item<5-> Pendulum: For a second-order description, observers \textcolor{red}{out} must become observers \textcolor{red}{in}.
+    		    \end{itemize}
+            \end{frame}
+            \begin{frame}{Design As Done}
+            \framesubtitle{Being Out of Control}
+    		    \begin{itemize}
+    		        \item<1-> Not being in control $\implies$ a way of increasing creativity
+                    \item<2-> Restricting responses and conversation to what I know\\
+                        $\implies$ Destroying conversation
+                        $\implies$ Conversation controlled by a participant $\longrightarrow \nexists$
+                    \item<3-> Design is a second-order activity: Ashby's law cannot be utilised.
+                    \item<4-> Stopping and re-starting? 
+                    \item<5-> Pendulum: For a second-order description, observers \textcolor{red}{out} must become observers \textcolor{red}{in}.
+    		    \end{itemize}
+            \end{frame}
+            \begin{frame}{Design As Done}
+            \framesubtitle{Complexity}
+    		    \begin{itemize}
+    		        \item<1-> What if the system (the problem under study) is transcomputable?
+                        \begin{enumerate}
+                            \item Changing the definitions of the context (simplifying)
+                            \item Transforming the notion of control: control-as-restricting
+                        \end{enumerate}
+    		        \item<1-> Designer: someone who faces \textcolor{red}{complexity} (and ambiguity)
+                    \item<2-> ``The systems theorist of the future, I suggest, must be an expert in how to simplify'' \\--- Ross Ashby
+                    \item<3-> ``Progress means simplifying, not complicating'' --- Bruno Munari (Italian Designer)
+                    \item<4-> Simplifying: a process by which complex requirements can be brought together within \textcolor{teal}{one}, \textcolor{teal}{unified}, \textcolor{teal}{unitary} form.
+                    \item<4-> Design brings to complexity an approach that is distinct from complexity science, which can lead to added value.
+    		    \end{itemize}
+            \end{frame}
+        \subsection{Criteria and Conditions}
+            \begin{frame}{From Cybernetics to Design}
+    		    \begin{itemize}
+    		        \item<1-> Design leads not to the best, but to a large variety of different outcomes, giving \textcolor{red}{choice}.
+    		        \item<2-> The nature of design conversation:\\
+    		        For it to operate $\implies \exists$ a listener (viewer)\\
+    		        To listen (see) $\implies \exists$ an open (and receptive) mind, and generosity\\
+    		        To design $\implies$ see the possibilities \textcolor{red}{not already existent} in the mind
+    		        To increase choices through design $\implies$ acting responsibly
+    		        \item<3-> Cybernetic systems work if we accept responsibility, and act generously, with an open mind.
+    		        \item<4-> Conversation is the intersection
+    		    \end{itemize}
+            \end{frame}
+        \subsection{Notes on Epistemology}
+            \begin{frame}{Knowledge Of and Knowledge For}
+    		    \begin{itemize}
+    		        \item<1-> Science \textcolor{red}{through an observer} gives us \textcolor{red}{knowledge of} the system. \\
+    		        Helps us understand \textcolor{red}{what is} $\longrightarrow$ passive and neutral \\
+    		        $\implies$ \textcolor{orange}{Tacit} knowledge
+    		        \item<2-> Designers are actors \textcolor{red}{in} the world $\longrightarrow$ require and generate \textcolor{red}{knowledge for} acting in the world as they make it.\\
+    		        $\implies$ \textcolor{teal}{Reflective} knowledge
+    		        \item<3-> Technology (engineering): converts `knowledge of' into `knowledge for'
+    		    \end{itemize}
+		    \end{frame}
+    \section{Discussion}
+        \begin{frame}{Wicked Problems}
+		    \centering\includegraphics[height=0.8\textheight]{resources/rittle.png}
+        \end{frame}
+        \begin{frame}{Cybernetics and Design: Conversations for Action \cite{Dubberly2019}}
+		    \centering\includegraphics<1>[page=31, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+		    \centering\includegraphics<2>[page=32, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+		    \centering\includegraphics<3>[page=33, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+		    \centering\includegraphics<4>[page=34, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+		    \centering\includegraphics<5>[page=35, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+		    \centering\includegraphics<6>[page=36, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+		    \centering\includegraphics<7>[page=37, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+		    \centering\includegraphics<8>[page=38, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+		    \centering\includegraphics<9>[page=39, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+        \end{frame}
+        \begin{frame}{Interaction \cite{pangaro_web}}
+    		\begin{figure}
+    		    \centering
+    		    \includegraphics<1>[height=0.75\textheight]{resources/interaction.PNG}
+    		    \centering
+    		    \includegraphics<2>[height=0.75\textheight]{resources/conversing1.png}
+    		    \centering
+    		    \includegraphics<3>[height=0.75\textheight]{resources/conversing2.png}
+    		\end{figure}
+        \end{frame}
+        \begin{frame}{Conversations? \cite{pangaro_web}}
             \centering\includegraphics<1>[page=35, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
@@
         \end{frame}
-    \section{The Harmony}
-        \
+        \begin{frame}{\cite{pangaro_web}}
+            \centering\includegraphics<1>[page=41, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<2>[page=42, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<3>[page=44, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<4>[page=89, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<5>[page=90, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+        \end{frame}
+        \begin{frame}{Implications \cite{pangaro_web}}
+            \centering\includegraphics<1>[page=92, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<2>[page=93, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<3>[page=94, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<4>[page=95, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<5>[page=96, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<6>[page=97, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<7>[page=98, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<8>[page=99, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<9>[page=100, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<10>[page=101, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<11>[page=102, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<12>[page=103, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<13>[page=104, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<14>[page=105, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<15>[page=106, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<16>[page=107, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<17>[page=108, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<18>[page=109, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<19>[page=110, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<20>[page=111, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<21>[page=112, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<22>[page=113, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<23>[page=114, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<24>[page=115, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<25>[page=127, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+            \centering\includegraphics<26>[page=128, width=0.75\textwidth]{resources/Pangaro_Vienna-HvF-Lecture_June-2017_distro-r.pdf}
+        \end{frame}
+        \begin{frame}{Design of Ethical Interfaces \cite{pangaro_web}}
+            \centering\includegraphics<1>[page=12, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<2>[page=13, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<3>[page=14, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<4>[page=15, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<5>[page=16, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<6>[page=17, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<7>[page=49, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<8>[page=18, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<9>[page=19, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<10>[page=20, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+            \centering\includegraphics<11>[page=21, width=0.75\textwidth]{resources/Pangaro-HCII_Seminar-April_2019-distro.pdf}
+        \end{frame}
 
-\section{References}
+    \section*{Overview}
+    	\begin{frame}
+		\frametitle{Overview}
+    		\tableofcontents
+    	\end{frame}
+
+\section*{References}
 	\begin{frame}[allowframebreaks]
@@
     \end{frame}
+    \begin{frame}{Interaction}
+        \framesubtitle{Forming an interaction - Meaning is PRIVATE}
+        \centering\includegraphics[height=0.75\textheight]{resources/interaction1.png}
+    \end{frame}
+    \begin{frame}{Relationship}
+        \framesubtitle{Interactions Flowing in Both Direction + Time + Recursion = TRUST}
+        \centering\includegraphics[height=0.75\textheight]{resources/interaction2.png}
+    \end{frame}
+    \begin{frame}{Conversation}
+        \framesubtitle{``Immaterial'' Aspects}
+        \centering\includegraphics[height=0.75\textheight]{resources/interaction3.png}
+    \end{frame}
     \begin{frame}{Mental Models}
@@
     \end{frame}
-    \begin{frame}{Interaction}
-        \framesubtitle{Configurations \cite{pangaro_web}}
-		\begin{figure}
-		    \centering
-		    \includegraphics[height=0.75\textheight]{resources/interaction.PNG}
-		\end{figure}
-    \end{frame}
 \end{document}
